---
title: "Assignment 2"
author: "YOUR NAME"
output: html_document
---

Please read all instructions carefully.  This helps us return your assignments as quickly as possible. 

  Click 'Save As', and rename the document with your blackboard username. 
  Fill in your name above.
  To allow this file to be knit, you might need to save it in a new location, as you do not have write permissions in the dropbox folder, and R does not work well with Chinese characters.
	Do not comment out the lines that produce output.  Check your html file before submission to ensure it has all relevant output.  
	Ensure all answers are your own words and your own work.  Do not delete anything below these instructions.  
	Before you submit, zip both the rmd and results html files.  Submit this on blackboard. 


**Question 1A:**
```{r Question 1A}
#INSERT CODE HERE
setwd("/Users/fanfan/Documents/2022fallB/GBA436R/Assignment2")
dt = read.csv("Facebook Data.csv", header=TRUE, sep=",")
summary(lm(clickPerDollar~factor(adType)+factor(category)+factor(placement)+factor(keywords)+factor(body)+ageMean, data = dt))
```


**Question 1B:**
```{r Question 1B}
#INSERT CODE HERE - WRITTEN ANSWER ON BLACKBOARD
#Comment out the line that gives you an error so that you can compile it
#summary(lm(clickPerDollar~date+factor(adType)+factor(category)+factor(placement)+factor(keywords)+factor(body)+ageMean, data = dt))
# Since it contains non-numeric and only one same independent value, it will fail to fit if there aren't at least 2 different non-numeric values for the linear regression.
```


**Question 1C:**
```{r Question 1C}
#INSERT CODE HERE
## The coefficient shows that, compared to the category "cosmetics", if we use category "general", the average click per dollar will decrease by 45.741606 times holding other elements unchanged.
```

**Question 1D:**
```{r Question 1D}
#INSERT CODE HERE - WRITTEN ANSWER ON BLACKBOARD
## The coefficient shows that when average age of the targeted consumers increase by 1 years old, the average click per dollar will increase by 2.598849 times holding other factors unchanged.
```


**Question 2A:**
```{r Question 2A}
#INSERT CODE HERE - WRITTEN ANSWER ON BLACKBOARD
summary(lm(clickPerDollar~factor(adType)+factor(category)+factor(placement)+factor(keywords)+factor(body)+ageMean+factor(category)*ageMean, data = dt))

### factor(category)eCom:ageMean
### When the average age of the targeted consumers is 0, when we shift the category from "cosmetics" to "ecom", the click per dollar will decrease for 0.36125 times on average.
```


**Question 2B:**
```{r Question 2B}
#INSERT CODE HERE - WRITTEN ANSWER ON BLACKBOARD
## The coefficient changes from -42.6 to -28.3. The coefficient is calculated when average age is 0 in 2a, but not in 1a and it decreases with the age increasing.
```